Ecuador plant occurrence data merging

### 2023-01-23 code/L2/L2_Ecuador_plant_occ.Rmd
add metadata file add summary code (same as L0)

# Load required packages
```{r}
library(bdc)
```

# Read in the configuration table
```{r}
metadata <-
  readr::read_csv(system.file("ADD FILE PATH HERE",
                              package = "bdc"),
                  show_col_types = FALSE)
```

# Read in BIEN, GBIF, and IUCN occurrence data
```{r}
# Path to the folder containing the example datasets. For instance:
path <- data_path

# Change in the Configuration table the path to the folder in your computer containing the example datasets
metadata$fileName <-
  gsub(pattern = "https://raw.githubusercontent.com/brunobrr/bdc/master/inst/extdata/input_files/",
       replacement = path,
       x = metadata$fileName)
```

```{r}
database <-
bdc_standardize_datasets(metadata = metadata,
                         format = "csv",
                         overwrite = TRUE,
                         save_database = TRUE)
```

>>>>

# Load required packages
```{r}
library(bdc)
library(DataExplorer)
library(summarytools)
library(bdvis)
```

# Read in the configuration table
```{r}
metadata <-
  readr::read_csv(file.path(data_path, "occ_metadata.csv"),
                  show_col_types = FALSE)
```

# Read in BIEN, GBIF, and IUCN occurrence data

```{r}
database <-
bdc_standardize_datasets(metadata = metadata,
                         format = "csv",
                         overwrite = TRUE,
                         save_database = FALSE)
```

# Summary of data
```{r}
summary(database)
```

### using DataExplorer package
```{r}
plot_str(database)
introduce(database)
plot_intro(database)
plot_missing(database)
```

### using summarytools package
```{r}
database_summary <- dfSummary(database, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(database_summary, method = "render")
view(database_summary, file = file.path(output_path,"database_summary.html"))
```

```{r}
#using bdvis package
d <- format_bdvis(d, , Latitude = "Latitude", Longitude = "Longitude", Date_collected = "Date_collected", Scientific_name = "AccSpeciesName")
bdsummary(d)
d$Date_collected <- as.Date(d$Date_collected)
bdcalendarheat(d)
getcellid(d, gridscale = 10)
distrigraph(d, ptype = "species")
distrigraph(d, ptype = "efforts")
distrigraph(d, ptype = "cell")
distrigraph(d, ptype = "effortspecies")
bdcomplete(d)
mapgrid(d, ptype = "species", region = "Ecuador")
```
